\documentclass[]{report}
% Title Page
\title{NATIONAL e-Passport REGISTRATION}
\author{{}\\
       {}\\
}
\begin{document}
\maketitle

\chapter*{BACKGROUND}
In the national Constitution of most nations, state that, “Every citizen shall have the right to a passport or other travel document”. It is therefore a constitutional right for every citizen to have a passport. The Ministry of Internal Affairs (MIA) and particularly the Directorate of Citizenship and Immigration Control (DCIC), is responsible for the issuance of passports in in a country. 
\paragraph{}
The processing of a passport is expected to take ten (10) working days or fourteen (14) calendar days. However, processing passports by the Passport Control Office (PCO) takes longer periods, with average delays of 9 to 32 days at the Ministry headquarters and in the regions/districts, respectively.   
\paragraph{}
This has resulted into public dissatisfaction with the service rendered by the government in this regard. The audit sought to ascertain the magnitude of the delays in the processing passports and to examine the underlying causes of the delays and suggest to the management recommendations that could improve its performance and  reduce the days taken to process passports. 
\paragraph{}
The delays were attributed to the unconventional citizenship verification procedures, manual processing of passports, inadequate communication strategy, poor records management and unfavourable staff working conditions. 


\chapter*{DATA COLLECTION}
 Data was collected through the following data collection methods:
 \paragraph{}
 \section*{Interviews}
 Interviews were held with senior officers in the Directorate of Citizenship and Immigration Control to obtain a general understanding of the processes involved in the issuance of passports and ascertain the causes of the delay in the processes. In addition, forty (40) clients and thirty (30) staff members in the PCO from the Ministry headquarters and the regions/districts were interviewed to ascertain the 
  \paragraph{}
  \section*{Observation}
Several regional/district immigration offices and the Ministry headquarters were visited with a view of observing how immigration officers were conducting business and to assess the level of clients’ satisfaction. The working environment of staff was also observed and assessed during the field visits. The audit team also observed the general work flow in the various sections of the Department. 
\paragraph{}
\section*{Document Review}
A number of documents and records were reviewed with an objective of understanding the processes, legal mandate, activities, laws and regulations involved in the issuance of passports. Also examined were application forms and passport registers. 


\end{document}          
